Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-08-26 manuscript/manuscript.Rmd
adds MBH edits to R1

\begin{enumerate}[label=\textbf{\arabic*}]
        \item Rapid environmental change has generated growing interest in forecasts of future population trajectories. Traditional population models built with detailed demographic observations from one study site can address the impacts of environmental change at particular locations, but are difficult to scale up to the landscape and regional scales relevant to management decisions. An alternative is to build models using population-level data which are much easier to collect than individual-level data over broad spatial scales. However, it is unknown whether models built using population-level data adequately capture the effects of density-dependence and environmental forcing that are necessary to generate skillful forecasts.
        \item Here, we test the consequences of aggregating individual responses when forecasting the population states \textcolor{blue}{(percent cover)} and trajectories of four perennial grass species in a semi-arid grassland in Montana, USA. We parameterized two population models for each species, one based on individual-level data (survival, growth and recruitment) and one on population-level data (percent cover), and compared their forecasting \textcolor{blue}{accuracy} and forecast horizons with and without the inclusion of climate covariates. For both models we used Bayesian ridge regression to weight the influence of climate covariates for optimal prediction. 
        \item In the absence of climate effects, we found no significant difference between the forecast \textcolor{blue}{accuracy} of models based on individual-level data and models based on population-level data. Climate effects were weak, but increased forecast \textcolor{blue}{accuracy} for two species. Increases in \textcolor{blue}{accuracy} with climate covariates were similar between model types.
        \item In our case study, percent cover models generated forecasts as \textcolor{blue}{accurate} as those from a demographic model. For the goal of forecasting, models based on aggregated individual-level data may offer a practical alternative to data-intensive demographic models. Long time series of percent cover data already exist for many plant species. Modelers should exploit these data to predict the impacts of environmental change.
    \end{enumerate}

@@

We compared the forecasting skill \textcolor{blue}{(accuracy and precision)} of statistical and population models based on aggregated, population-level data with the skill of models based on individual-level data. We used a demographic dataset that tracks the fates of individual plants from four species over 14 years to build two kinds of single-species population models, traditional models using individual growth, survival, and recruitment data and alternative models based on population-level (basal cover) data. We simulated the models to answer two questions motivated by the fact that the effects of intraspecific competition (density dependence) and interannual weather variability act at the level of the individual [@Clark2011b].
First, can population models fit using aggregated individual-level data (percent cover) adequately capture density dependence to produce forecasts as skillful as those from models fit to demographic data? 
Second, can population models fit using aggregated data adequately capture the influence of climate on population growth and, in turn, produce forecasts as skillful as those from models fit to demographic data?

Materials and Methods
---------------------
### Overview of analysis
\textcolor{blue}{Below we describe our focal plant populations, the population models we use to make predictions, and how we compare model forecasts, but offer a brief overview here.
We used two types of data: individual-level data and percent cover data.
Using the individual-level data we fit three vital rate regressions (survival, growth, and rectruitment) to build an Integral Projection Model (IPM) for simulating the plant populations.
Using the percent cover data we fit a simple, Gompertz-style population growth model, which we refer to as a quadrat-based model (QBM).
Both model types (IPM and QBM) we fit and simulate versions with and without climate covariates.
We used Bayesian ridge regression to weight the importance of each climate covariate.
We then performed cross-validation to assess each model's ability to predict out-of-sample data.
We compared the forecast accuracy ($\rho$, correlation between observations and predictions) and mean absolute error (MAE) between the IPM and the QBM to test our expectation that the IPM should outperform the QBM.
Lastly, we use in-sample forecasts to quantify each model's forecast horizon} [@Petchey2015].

### Study site and data
Our demographic data come from a northern mixed grass prairie at the Fort Keogh Livestock and Range Research Laboratory near Miles City, Montana, USA ($46^{\circ}$ 19' N, $105^{\circ}$ 48' W). The dataset is available on Ecological Archives[^link] [@Anderson2011], and interested readers should refer to the metadata for a complete description. The site is 800 m above sea level and mean annual precipitation (1878-2009) is 334 mm, with most annual precipitation falling from April through September. The community is grass-dominated, and we focused on the four most abundant grass species: \emph{Bouteloua gracilis} (BOGR), \emph{Hesperostipa comata} (HECO), \emph{Pascopyrum smithii} (PASM), and \emph{Poa secunda} (POSE) (Fig. 1 and Table 1). *B. gracilis* is a warm-season perennial grass, whereas *H. comata*, *P. smithii*, and *Poa secunda* are cool-season perennial grasses. The growing season begins in early spring (typically in April) and lasts through mid-summer (typically in June).

@@

From 1932 to 1945, individual plants were identified and mapped annually in 44 1-$\text{m}^2$ quadrats using a pantograph. The quadrats were distributed among six pastures, each assigned a grazing treatment of light (1.24 ha/animal unit month), moderate (0.92 ha/aum), and heavy (0.76 ha/aum) stocking rates (two pastures per treatment). In this analysis, we accounted for potential differences among the grazing treatments, but do not focus on grazing$\times$climate interactions. The annual maps of the quadrats were digitized and the fates of individual plants tracked and extracted using a computer program [@Lauenroth2008; @Chu2014a]. The permanent quadrats have not been relocated, but their distribution in six different pastures means the data represent a broad spatial distribution for the study area. Daily climate data are available for the duration of the data collection period (1932 - 1945) from the Miles City airport, Wiley Field, 9 km from the study site.

We modeled each grass population based on two levels of data: individual and quadrat. The individual data are the "raw" data. For the quadrat-level data we simply sum individual basal cover for each quadrat by species. This is equivalent to a near-perfect census of quadrat percent cover because measurement error at the individual-level is small [@Chu2015]. Based on these two datasets of 13 year-to-year transitions, we can compare population models built using individual-level data and aggregated, quadrat-level data. At the individual level, we explicitly model three vital rates: growth, survival, and recruitment. At the quadrat level, we model population growth as change in percent cover of quadrats with non-zero cover in year *t* and in year *t-1*, ignoring within-quadrat extirpation and colonization events because they are very rare in our time series ($N=16$ and $N=13$, respectively, across all species). Sample sizes for each species and vital rate model are shown in Table 1.

@@

### Model fitting and statistical regularization
####  Model fitting
Our Bayesian approach to fitting the vital rate models required choosing appropriate priors for unknown parameters and deciding which, if any, of those priors should be hierarchical. For each species, we fit yearly size effects and yearly intercepts hierarchically, where year-specific coefficients were drawn from global distributions representing the mean size effect and intercept. Quadrat random effects were also fit hierarchically, with quadrat offsets being drawn from distributions with mean zero and a shared variance term (independent Gaussian priors). Climate effects were modeled as independent covariates whose prior distributions were optimized for prediction using statistical regularization (see **Statistical regularization: Bayesian ridge regression** below).

All of our analyses (model fitting and simulating) were conducted in R [@R2013]. We used the 'No-U-Turn' Hamiltonian Monte Carlo sampler in Stan [@stan2014]  to estimate the posterior distributions of model parameters using the package `rstan` [@rstan2014]. We obtained posterior distributions for all model parameters from three parallel MCMC chains run for 1,000 iterations after discarding an initial 1,000 iterations. Such short MCMC chains are possible because the Stan sampler reduces the number of iterations needed to achieve convergence. We assessed convergence visually and checked that scale reduction factors for all parameters were less than 1.1. There were six instances where the scale reduction factor for a particular parameter was greater than 1.1. In those cases, we checked the traceplots of the violating parameter and discovered that one chain, out of three, was poorly behaved. Therefore, we removed that chain from the analysis, leaving two well-mixed and converged chains for those six parameters. For the purposes of including parameter uncertainty in our population models, we retained the final 1,000 iterations from each of the three MCMC chains to be used as randomly drawn values during population simulation. We report the posterior mean, standard deviation, and 95% Bayesian Credible Intervals for every parameter of each model for each species in the Supporting Information (Tables S5-S20).

#### Statistical regularization: Bayesian ridge regression
For models with climate covariates, our objective is to model the response of our focal grass species to interannual variation in climate, even if those responses are weak.
Therefore, we avoid selecting among models with all possible combinations of climate covariates, and instead use Bayesian ridge regression to regulate, or constrain, the posterior distributions of each climate covariate [@Gerber2015; @Hooten2015].
Ridge regression is a specific application of statistical regularization that seeks to optimize model generality by trading off bias and variance.
As the name implies, statistical regularization involves the use of a regulator that constrains an optimization.
The natural regulator in a Bayesian application is the prior on the coefficient of interest.
Each of our statistical models includes the effects of climate covariates via the term $\textbf{z}'_t \boldsymbol{\beta}_c$ with prior $\boldsymbol{\beta}_c \sim \text{Normal}(\boldsymbol{\mu}_{\beta_c}, \sigma_{\beta_c}^2\textbf{I})$.
Because we standardized all climate covariates to have mean zero and variance one, we set $\boldsymbol{\mu}_{\beta_c} = 0$ and let $\sigma_{\beta_c}^2$ serve as the regulator that shrinks covariates toward zero -- the smaller the prior variance, the more the posteriors of $\boldsymbol{\beta}_c$ are shrunk toward zero, and the stronger the penalty [@Hooten2015].

@@

\vspace{-3em}
\begin{align}
\sum_{t=1}^T \text{log}_e \left(\frac{1}{S} \sum^S_{s=1}(y_{t,\text{hold}}|\theta_{ts})  \right).
\end{align}
\vspace{-3em}

@@

### Population models
Using samples from the posterior distribution of the vital rate statistical models, it is straightforward to simulate the population models. We used an Integral Projection Model (IPM) to simulate populations based on individual-level data [@Ellner2006] and a quadrat-based version of an individually-based model (Quadrat-Based Model, QBM) to simulate populations based on quadrat-level data. We describe each in turn.

@@

We used random draws from the final 1,000 iterations from each of three MCMC chains for each vital rate regression to carry-through parameter uncertainty into our population models. At each time step, we drew the full parameter set (climate effects and density-dependence fixed effects) from a randomly selected MCMC iteration. Relatively unimportant climate covariates (those that broadly overlap 0) will have little effect on the mean of the simulation results, but can contribute to their variation. To retain temporal variation associated with random year effects, we used posterior estimates of the mean temporal effect and the standard deviation of that effect to generate a random year effect for unobserved years. That is, for some future year *T*, the intercept is $\beta_{0,T} \sim \text{Normal}(\beta_0, \sigma_{\beta_0})$ and the effect of size is $\beta_{s,T} \sim \text{Normal}(\beta_s, \sigma_{\beta_s})$.

@@

### Forecast horizons
An important feature of any forecasting model is the rate at which forecast skill declines as the time between an observation and a forecast increases.
\textcolor{blue}{In particular, we are interested in the temporal distance at which forecast skill falls below a threshold: the so-called ecological forecast horizon} [@Petchey2015].
To assess the forecast horizons of our models, we initiate the forecast model with the population state at some time *t* and make sequential forecasts of the population at times $t+1, t+2, \dots, t+T$ where *T* is the maximum number of years between the initial year and the final year of our observations.
For example, if we initialize the forecast model with percent cover in 1940, we are able to make five forecasts up to the year 1945.
Forecast models are not re-initialized with observations between years.
Thus, in our current example, the model forecast for percent cover in 1941 has a forecast horizon of one year, the forecast in 1942 has a forecast horizon of two years, and so on.
We performed these simulations for all model types (IPM with/without climate; QBM with/without climate) using mean parameter values for all possible initial years.
For a given forecast distance, we averaged the correlation between forecasts and observations.
Note that these forecasts are all made using in-sample data because we used model fits from the full data set.
Nonetheless, these simulations offer insight into the differences among model forecast horizons.
\textcolor{blue}{We chose a forecast accuracy of $\rho = 0.5$ as our forecast proficiency threshold.
So, the forecast horizon is the temporal distance at which forecast accuracy falls below $\rho = 0.5$.}

Results
-------
The IPM and QBM generated one-step-ahead forecasts of similar skill for out-of-sample observations, with an average correlation between predictions and observations ($\rho$) of 0.72 across all models and species (Fig. 2).
Without climate covariates, the accuracy of forecasts from the IPM were not statistically greater than the accuracy of forecasts from the QBM (Fig. 2) and overall error was similar (mean absolute error; Fig. S1, Supporting Information).
With climate covariates, the best out-of-sample predictive model (highest *lppd*) for each species and vital rate typically resulted from highly constrained priors on the climate effects (Fig. S2, Supporting Information).
Thus, the posterior distributions of climate effects included in our models overlapped zero and generally shrunk toward zero, though for some species-vital rate combinations, important effects (80% credible interval does not include zero) did emerge (Fig. 3).

@@

With climate covariates included \textcolor{blue{and using mean parameter values, the accuracy of both models' forecasts declined as the distance between the last observation and the forecast increased}, but they did so at similar rates (Fig. 4).
The only exception is for *Poa secunda*, where QBM forecast accuracy remained steady as the \textcolor{blue}{temporal distance of the forecast increased}, whereas IPM forecast accuracy declined (Fig. 4).
\textcolor{blue}{The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (Table S23).
Likewise, the QBM was rarely more accurate the IPM, the only exception being for \emph{H. comata} at temporal distances of two ($t_{(115)}$ = 2.39, \emph{P} = 0.002) and three years ($t_{(98)}$ = 2.04, \emph{P} = 0.022) (Table S24).
There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast profieciency threshold by a large margin (Fig. 4, Table S24).}

@@

Our comparison of a traditional, demographic population model without environmental forcing (the IPM) to an equivalent model inspired by density-structured models (the QBM) showed that, generally, IPM forecasts of out-of-sample plant population states were no more accurate than forecasts from the QBM (Fig. 2; `no-climate' bars).
This result overturned our expectation that the IPM would out-perform the QBM, thanks to its mechanistic representation of the perennial life cycle, and confirms theoretical [@Freckleton2011] and empirical work [@Taylor2004; @Queenborough2011] showing that density-structured models can be useful surrogates for demographic models when the goal is to estimate or forecast population states over large spatial extents.

We also expected the inclusion of environmental forcing to reveal more differences between the models.
Interannual variation in weather can affect vital rates in different ways [@Dalgleish2011], so, estimates of climate effects on plant population growth may be biased or non-identifiable when the underlying statistical model is fit using population-level data that integrates over the potentially unique climate responses of individual vital rates.
We found some evidence that the QBM failed to detect climate effects for three species (*B. gracilis*, *H. comata*, and *Poa secunda*), where important climate effects were identified in the individual vital rate models but not in the percent cover model (Fig. 3).
However, for the two species where including climate covariates increased forecast accuracy (*B. gracilis* and *Poa secunda*), forecast skill (Fig. 2) and error (Fig. S2) were equivalent between the IPM and QBM.

The higher accuracy of the IPM and QBM with climate covariates for *B. gracilis* and *Poa secunda*  highlights the advantage of contemporary modeling and variable selection approaches such as ridge regression and LASSO over techniques that would exclude "non-significant" effects from final models.
Ridge regression allows researchers to retain covariates whose effects may be difficult to identify in noisy data or short time series.
This is especially important when forecasting the impacts of climate variability, where it is important to include to effects of forcing variables (e.g., temperature and precipitation) even if such effects are difficult to identify.
Indeed, we failed to detect strong climate effects in the QBM for *B. gracilis* and *Poa secunda*, but including climate covariates still improved forecasting skill (Fig. 2).
If a species is truly unresponsive to a given climate variable, statistical regularization techniques will shrink the mean and variance of a covariate estimate toward zero [@Hooten2015].
Of course, no matter what model selection approach is adopted, a critical step is identifying the appropriate candidate covariates, which we attempted to do based on our knowledge of this semi-arid plant community.
However, the climate covariates we chose required aggregating daily weather data over discrete time periods.
It is possible that we did not choose the optimal time periods over which to aggregate.
New methods using functional linear models (or splines) may offer a data-driven approach for identifying the appropriate time periods over which to aggregate to produce a tractable set of candidate climate variables [@Teller2016].

We also expected IPM forecast accuracy to decline at a lower rate than the QBM as the \textcolor{blue}{time between the last observation and the forecast increased.}
In principle, more mechanistic models should produce better predictions, especially under novel conditions [@Evans2012b; @Schindler2015b].
In our case, the IPM explicitly models the influence of weather on recruitment and survival, effects that may be poorly represented in the QBM because recruitment and survival mainly affect small plants that contribute little to year-to-year changes in percent cover.
Over time, of course, the addition and subtraction of small plants can have large effects on population growth, so explicitly modeling these effects could contribute to a longer forecast horizon. 
However, we found no evidence \textcolor{blue}{that the forecast horizon for the IPM was greater than the QBM (Fig. 4).
On the contrary, the QBM tended to have a slightly longer forecast horizon than the IPM for most species (Fig. 4).
The QBM has fewer processes, so may better capture near term dynamics when populations do not fluctuate widely, as in our case.
When populations do not fluctuate widely, often the best forecast for population size at \emph{t+1} is the size at time \emph{t}.
Thus, a simpler model such as the QBM may be well-suited for predicting populations that fluctuate mildly around an equilibrium.}

>>>>

\begin{enumerate}[label=\textbf{\arabic*}]
        \item Rapid environmental change has generated growing interest in forecasts of future population trajectories. Traditional population models built with detailed demographic observations from one study site can address the impacts of environmental change at particular locations, but are difficult to scale up to the landscape and regional scales relevant to management decisions. An alternative is to build models using population-level data that are much easier to collect than individual-level data over broad spatial scales. However, it is unknown whether models built using population-level data adequately capture the effects of density-dependence and environmental forcing that are necessary to generate skillful forecasts.
        \item Here, we test the consequences of aggregating individual responses when forecasting the population states \textcolor{blue}{(percent cover)} and trajectories of four perennial grass species in a semi-arid grassland in Montana, USA. We parameterized two population models for each species, one based on individual-level data (survival, growth and recruitment) and one on population-level data (percent cover), and compared their forecasting \textcolor{blue}{accuracy} and forecast horizons with and without the inclusion of climate covariates. For both models, we used Bayesian ridge regression to weight the influence of climate covariates for optimal prediction. 
        \item In the absence of climate effects, we found no significant difference between the forecast \textcolor{blue}{accuracy} of models based on individual-level data and models based on population-level data. Climate effects were weak, but increased forecast \textcolor{blue}{accuracy} for two species. Increases in \textcolor{blue}{accuracy} with climate covariates were similar between model types.
        \item In our case study, percent cover models generated forecasts as \textcolor{blue}{accurate} as those from a demographic model. For the goal of forecasting, models based on aggregated individual-level data may offer a practical alternative to data-intensive demographic models. Long time series of percent cover data already exist for many plant species. Modelers should exploit these data to predict the impacts of environmental change.
    \end{enumerate}

@@

We compared the forecasting skill \textcolor{blue}{(accuracy and precision)} of statistical and population models based on aggregated, population-level data with the skill of models based on individual-level data. We used a demographic dataset that tracks the fates of individual plants from four species over 14 years to build two kinds of single-species population models, traditional models using individual growth, survival, and recruitment data and alternative models based on population-level (basal cover) data. We simulated from the models to answer two questions motivated by the fact that the effects of intraspecific competition (density dependence) and interannual weather variability act at the level of the individual [@Clark2011b].
First, can population models fit using aggregated individual-level data (percent cover) adequately capture density dependence to produce forecasts as skillful as those from models fit to demographic data? 
Second, can population models fit using aggregated data adequately capture the influence of climate on population growth and, in turn, produce forecasts as skillful as those from models fit to demographic data?

Materials and Methods
---------------------
### Overview of analysis
\textcolor{blue}{We used two types of data: individual-level data and percent cover data.
Using the individual-level data, we fit three vital rate regressions (survival, growth, and rectruitment) to build an Integral Projection Model (IPM) for simulating the plant populations.
Using the percent cover data we fit a simple, Gompertz population growth model, which we refer to as a quadrat-based model (QBM).
Both model types (IPM and QBM) were fit with and without climate covariates.
We used Bayesian ridge regression to weight the importance of each climate covariate.
We then performed cross-validation to assess each model's ability to predict out-of-sample data.
We compared the forecast accuracy ($\rho$, correlation between observations and predictions) and mean absolute error (MAE) between the IPM and the QBM to test our expectation that the IPM should outperform the QBM.
Lastly, we use in-sample forecasts to quantify each model's forecast horizon} [@Petchey2015].

### Study site and data
Our demographic data were obtained from a northern mixed grass prairie at the Fort Keogh Livestock and Range Research Laboratory near Miles City, Montana, USA ($46^{\circ}$ 19' N, $105^{\circ}$ 48' W). The dataset is available on Ecological Archives[^link] [@Anderson2011], and interested readers should refer to the metadata for a complete description. The site is 800 m above sea level and mean annual precipitation (1878-2009) is 334 mm, with most annual precipitation falling from April through September. The community is grass-dominated, and we focused on the four most abundant grass species: \emph{Bouteloua gracilis} (BOGR), \emph{Hesperostipa comata} (HECO), \emph{Pascopyrum smithii} (PASM), and \emph{Poa secunda} (POSE) (Fig. 1 and Table 1). *B. gracilis* is a warm-season perennial grass, whereas *H. comata*, *P. smithii*, and *Poa secunda* are cool-season perennial grasses. The growing season begins in early spring (typically in April) and lasts through mid-summer (typically in June).

@@

From 1932 to 1945, individual plants were identified and mapped annually in 44 1-$\text{m}^2$ quadrats using a pantograph. The quadrats were distributed among six pastures, each assigned a grazing treatment of light (1.24 ha/animal unit month), moderate (0.92 ha/aum), and heavy (0.76 ha/aum) stocking rates (two pastures per treatment). In this analysis, we accounted for potential differences among the grazing treatments, but do not focus on grazing$\times$climate interactions. The annual maps of the quadrats were digitized and the fates of individual plants tracked and extracted using a computer program [@Lauenroth2008; @Chu2014a]. The permanent quadrats have not been relocated, but their distribution in six different pastures implies that the data represent a broad spatial distribution for the study area. Daily climate data are available for the duration of the data collection period (1932 - 1945) from the Miles City airport, Wiley Field, 9 km from the study site.

We modeled each grass population based on two levels of data: individual and quadrat. The individual data are the "raw" data. For the quadrat-level data, we summed individual basal cover for each quadrat by species. This is equivalent to a near-perfect census of quadrat percent cover because measurement error at the individual-level is small [@Chu2015]. Based on these two datasets of 13 year-to-year transitions, we can compare population models built using individual-level data and aggregated, quadrat-level data. At the individual level, we explicitly model three vital rates: growth, survival, and recruitment. At the quadrat level, we model population growth as change in percent cover of quadrats with non-zero cover in year *t* and in year *t-1*, ignoring within-quadrat extirpation and colonization events because they are very rare in our time series ($N=16$ and $N=13$, respectively, across all species). Sample sizes for each species and vital rate model are shown in Table 1.

@@

### Model fitting and statistical regularization
####  Model fitting
Our Bayesian approach to fitting the vital rate models required choosing appropriate priors for unknown parameters and deciding which, if any, of those priors should be hierarchical. For each species, we fit yearly size effects and yearly intercepts hierarchically, where year-specific coefficients were modeled with global distributions representing the mean size effect and intercept. Quadrat random effects were also fit hierarchically, with quadrat offsets modeled with distributions with mean zero and a shared variance term (independent Gaussian priors). Climate effects were modeled as independent covariates whose prior distributions were optimized for prediction using statistical regularization (see **Statistical regularization: Bayesian ridge regression** below).

All of our analyses (model fitting and simulating) were conducted in R [@R2013]. We used the 'No-U-Turn' Hamiltonian Monte Carlo sampler in Stan [@stan2014]  to sample from the posterior distribution of model parameters using the package `rstan` [@rstan2014]. We obtained samples from the posterior distribution for all model parameters from three parallel MCMC chains run for 1,000 iterations after discarding an initial 1,000 iterations. Such short MCMC chains are possible because the Stan sampler reduces the number of iterations needed to achieve convergence. We assessed convergence visually and checked that scale reduction factors for all parameters were less than 1.1. For the purposes of including parameter uncertainty in our population models, we retained the final 1,000 iterations from each of the three MCMC chains to be used as randomly drawn values during population simulation. We report the posterior mean, standard deviation, and 95% Bayesian Credible Intervals for every parameter of each model for each species in the Supporting Information (Tables S5-S20).

<!--
There were six instances where the scale reduction factor for a particular parameter was greater than 1.1. In those cases, we checked the traceplots of the violating parameter and discovered that one chain, out of three, was poorly behaved. Therefore, we removed that chain from the analysis, leaving two well-mixed and converged chains for those six parameters. 
-->

#### Statistical regularization: Bayesian ridge regression
For models with climate covariates, our objective is to model the response of our focal grass species to interannual variation in climate, even if those responses are weak.
Therefore, we avoid selecting among models with all possible combinations of climate covariates, and instead use Bayesian ridge regression to regulate, or constrain, the posterior distributions of each climate covariate [@Gerber2015; @Hooten2015].
Ridge regression is a specific application of statistical regularization that seeks to optimize model generality by trading off bias and variance.
As the name implies, statistical regularization involves the use of a regulator that constrains an optimization.
The natural regulator in a Bayesian application is the prior on the coefficients of interest.
Each of our statistical models includes the effects of climate covariates via the term $\textbf{z}'_t \boldsymbol{\beta}_c$ with prior $\boldsymbol{\beta}_c \sim \text{Normal}(\boldsymbol{\mu}_{\beta_c}, \sigma_{\beta_c}^2\textbf{I})$.
Because we standardized all climate covariates to have mean zero and variance one, we set $\boldsymbol{\mu}_{\beta_c} = 0$ and let $\sigma_{\beta_c}^2$ serve as the regulator that shrinks covariate effects toward zero -- the smaller the prior variance, the more the posteriors of $\boldsymbol{\beta}_c$ are shrunk toward zero, and the stronger the penalty [@Hooten2015].

@@

\vspace{-3em}
\begin{align}
\sum_{t=1}^T \text{log}_e \left(\frac{1}{S} \sum^S_{s=1}[y_{t,\text{hold}}|\theta_{ts}]  \right).
\end{align}
\vspace{-3em}

@@

### Population models
Using samples from the posterior distribution of the vital rate statistical models, it is straightforward to simulate the population models. We used an Integral Projection Model (IPM) to simulate populations based on individual-level data [@Ellner2006] and a quadrat-based version of an individually-based model (Quadrat-Based Model, QBM) to simulate populations based on quadrat-level data. We describe each in what follows.

@@

We used random draws from the final 1,000 iterations from each of three MCMC chains for each vital rate regression to carry-through parameter uncertainty into our population models. At each time step, we drew the full parameter set (climate effects and density-dependence fixed effects) from a randomly selected MCMC iteration. Relatively unimportant climate covariates (those that broadly overlap 0) will have little effect on the mean of the simulation results, but can contribute to their variation. To retain temporal variation associated with random year effects, we used posterior estimates of the mean temporal effect and the standard deviation of that effect to generate a random year effect for unobserved years. That is, for some future year *T*, the intercept is $\beta_{0,T} \sim \text{Normal}(\beta_0, \sigma_{\beta_0}^2)$ and the effect of size is $\beta_{s,T} \sim \text{Normal}(\beta_s, \sigma_{\beta_s}^2)$.

@@

### Forecast horizons
An important feature of any forecasting model is the rate at which forecast skill declines as the time between an observation and a forecast increases.
\textcolor{blue}{In particular, we are interested in the temporal distance at which forecast skill falls below a threshold: the so-called ecological forecast horizon} [@Petchey2015].
To assess the forecast horizons of our models, we initiate the forecast model with the population state at some time *t* and make sequential forecasts of the population at times $t+1, t+2, \dots, t+T$ where *T* is the maximum number of years between the initial year and the final year of our observations.
For example, if we initialize the forecast model with percent cover in 1940, we are able to make five forecasts up to the year 1945.
Forecast models are not re-initialized with observations between years.
Thus, in our current example, the model forecast for percent cover in 1941 has a forecast horizon of one year, the forecast in 1942 has a forecast horizon of two years, and so on.
We performed these simulations for all model types (IPM with/without climate; QBM with/without climate) using mean parameter values for all possible initial years.
For a given forecast distance, we averaged the correlation between forecasts and observations.
Note that our forecasts for the horizon analysis are all made using in-sample data because we used model fits from the full data set.
Nonetheless, our simulations offer insight into the differences among model forecast horizons.
\textcolor{blue}{We chose a forecast accuracy of $\rho = 0.5$ as our forecast proficiency threshold.
So, the forecast horizon is the temporal distance at which forecast accuracy falls below $\rho = 0.5$.}

Results
-------
The IPM and QBM generated one-step-ahead forecasts of similar skill for out-of-sample observations, with an average correlation between predictions and observations ($\rho$) of 0.72 across all models and species (Fig. 2).
Without climate covariates, the accuracy of forecasts from the IPM were not statistically greater than the accuracy of forecasts from the QBM (Fig. 2) and overall error was similar (mean absolute error; Fig. S1, Supporting Information).
With climate covariates, the best out-of-sample predictive model (highest *lppd*) for each species and vital rate typically resulted from highly constrained priors on the climate effects (Fig. S2, Supporting Information).
Thus, the posterior distributions of climate effects included in our models overlapped zero and generally were shrunk toward zero, though for some species-vital rate combinations, important effects (80% credible interval does not include zero) did emerge (Fig. 3).

@@

With climate covariates included \textcolor{blue}{and using mean parameter values, the accuracy of both models' forecasts declined as the distance between the last observation and the forecast increased}, but they did so at similar rates (Fig. 4).
The only exception is for *Poa secunda*, where QBM forecast accuracy remained steady as the \textcolor{blue}{temporal distance of the forecast increased}, whereas IPM forecast accuracy declined (Fig. 4).
\textcolor{blue}{The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (Table S23).
Likewise, the QBM was rarely more accurate the IPM, the only exception being for \emph{H. comata} at temporal distances of two ($t_{(115)}$ = 2.39, \emph{P} = 0.002) and three years ($t_{(98)}$ = 2.04, \emph{P} = 0.022) (Table S24).
There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast profieciency threshold by a large margin (Fig. 4, Table S24).}

@@

Our comparison of a traditional, demographic population model without environmental forcing (the IPM) to an equivalent model inspired by density-structured models (the QBM) showed that, generally, IPM forecasts of out-of-sample plant population states were no more accurate than forecasts from the QBM (Fig. 2; `no-climate' bars).
This result differed from our expectation that the IPM would out-perform the QBM, because of its mechanistic representation of the perennial life cycle.
Our result also confirms theoretical [@Freckleton2011] and empirical work [@Taylor2004; @Queenborough2011] showing that density-structured models can be useful surrogates for demographic models when the goal is to estimate or forecast population states over large spatial extents.

We also expected the inclusion of environmental forcing to reveal more differences between the models.
Interannual variation in weather can affect vital rates in different ways [@Dalgleish2011].
Thus, estimates of climate effects on plant population growth may be biased or non-identifiable when the underlying statistical model is fit using population-level data that integrates over the potentially unique climate responses of individual vital rates.
We found some evidence that the QBM failed to detect climate effects for three species (*B. gracilis*, *H. comata*, and *Poa secunda*), where important climate effects were identified in the individual vital rate models but not in the percent cover model (Fig. 3).
However, for the two species where including climate covariates increased forecast accuracy (*B. gracilis* and *Poa secunda*), forecast skill (Fig. 2) and error (Fig. S2) were equivalent between the IPM and QBM.

The higher accuracy of the IPM and QBM with climate covariates for *B. gracilis* and *Poa secunda*  highlights the advantage of contemporary modeling and variable selection approaches such as ridge regression and LASSO over techniques that would exclude "non-significant" effects from final models.
Ridge regression allows researchers to retain covariates whose effects may be difficult to identify in noisy data or short time series.
This is especially important when forecasting the impacts of climate variability, where it is important to include the effects of forcing variables (e.g., temperature and precipitation) even if such effects are difficult to identify.
Indeed, we failed to detect strong climate effects in the QBM for *B. gracilis* and *Poa secunda*, but including climate covariates still improved forecasting skill (Fig. 2).
If a species is truly unresponsive to a given climate variable, statistical regularization techniques will shrink the mean and variance of a covariate estimate toward zero [@Hooten2015].
Of course, regardless of what model selection approach is adopted, a critical step is identifying the appropriate candidate covariates, which we attempted to do based on our knowledge of this semi-arid plant community.
However, the climate covariates we chose required aggregating daily weather data over discrete time periods.
It is possible that we did not choose the optimal time periods over which to aggregate.
New methods using functional linear models (or splines) may offer a data-driven approach for identifying the appropriate time periods over which to aggregate to produce a tractable set of candidate climate variables [@Sims2007; @VandePol2011; @Teller2016].

We also expected IPM forecast accuracy to decline at a lower rate than the QBM as the \textcolor{blue}{time between the last observation and the forecast increased.}
In principle, more mechanistic models should produce better predictions, especially under novel conditions [@Evans2012b; @Schindler2015b].
In our case, the IPM explicitly models the influence of weather on recruitment and survival, effects that may be poorly represented in the QBM because recruitment and survival mainly affect small plants that contribute little to year-to-year changes in percent cover.
Over time, the addition and subtraction of small plants can have large effects on population growth, thus, explicitly modeling these effects could contribute to a longer forecast horizon. 
However, we found no evidence \textcolor{blue}{that the forecast horizon for the IPM was greater than the QBM (Fig. 4).
On the contrary, the QBM tended to have a slightly longer forecast horizon than the IPM for most species (Fig. 4).
The QBM has fewer processes, thus it may better capture near term dynamics when populations do not fluctuate widely, as in our case.
When populations do not fluctuate widely, often the best forecast for population size at \emph{t+1} is the size at time \emph{t}.
Thus, a simpler model such as the QBM may be well-suited for predicting populations that fluctuate mildly around an equilibrium.}

Our comparison of a model based on individual-level data with one based on percent cover data is not an exhaustive test.
Understanding the reasons why the percent cover-based model matched the skill of a demographic model for our focal species may help us anticipate situations in which a percent-cover approach would fail. 
First, for none of our species did a climate covariate have a strong negative effect on one vital rate and a strong positive effect on a different vital rate (Fig. 3).
As noted by @Freckleton2011, complex age or stage structure can compromise predictions from models that aggregate over life-histories, and the same should be true when aggregating across vital rates with contrasting responses to climate drivers.
Second, our particular recruitment model is already so aggregated -- it averages across seed production, germination and establishment -- that it may fail to detect important demographic responses to climate, putting our individual-based model and percent cover model on more equal footing. 
More finely resolved recruitment data might help our individual-based model outperform the population-level model.
As advocated by @Freckleton2011, knowledge of a species' population ecology should guide the modeling approach.
\textcolor{blue}{Third, our percent cover data are essentially error-free because we were able to aggregate indiviual plant areas to calculate percent cover.
Percent cover data collected by typical sampling protocals (e.g., Daubenmire frames) will include error that may affect population forecasts due to misspecifing the initial conditions and/or biasing model parameters} [@Queenborough2011].
\textcolor{blue}{Thus, it may be that our percent cover model performed just as well as the individual-based model because percent cover was perfectly measured.
One way to account for such error is to develop a sampling model that relates the observations (estimated percent cover in a plot) to the true state (percent cover derived from individual plant measurements in the same plot)} [@Hobbs2015].
